\LARGE \bf Expectation-Maximization based defense mechanism for distributed Model Predictive Control

### 2022-02-15 article/article.tex
change wrong superscript and submit

The $P_{i}^{n}$ are constructed using $H_{i}$ and $\bar{\Gamma}_{i}$; and $\vec{s}_{i}^{j}$ are constructed using $H_{i}$, $\fik$ and $\bar{\Gamma}_{i}$. The specific construction depends on the active constraints in~\eqref{eq:constraints}.
For example, if all constraints are active, we have ${P_{i}^{\text{ac}}={(\bar{\Gamma}_{i}H_{i}^{-1}\bar{\Gamma}_{i}\T)}^{-1}}$ and ${\vec{s}_{i}^{\text{ac}}[k]=P_{i}^{1}\bar{\Gamma}_{i}H_{i}^{-1}\fik}$.
Futhermore, if all constraints are inactive, we have ${P_{i}^{\text{in}}=0_{c\times c}}$ and ${\vec{s}_{i}^{\text{in}}=\0_{c}}$.

>>>>

The $P_{i}^{n}$ are constructed using $H_{i}$ and $\bar{\Gamma}_{i}$; and $\vec{s}_{i}^{j}$ are constructed using $H_{i}$, $\fik$ and $\bar{\Gamma}_{i}$. The specific construction depends on the active constraints in~\eqref{eq:constraints}.
For example, if all constraints are active, we have ${P_{i}^{\text{ac}}={(\bar{\Gamma}_{i}H_{i}^{-1}\bar{\Gamma}_{i}\T)}^{-1}}$ and ${\vec{s}_{i}^{\text{ac}}[k]=P_{i}^{\text{ac}}\bar{\Gamma}_{i}H_{i}^{-1}\fik}$.
Futhermore, if all constraints are inactive, we have ${P_{i}^{\text{in}}=0_{c\times c}}$ and ${\vec{s}_{i}^{\text{in}}=\0_{c}}$.
